Title Goes Here

### 2021-04-08 analysis/paper/shceof.Rmd
Muestra mejor significancia en SAm-vertical

sam_r2 %>%
  .[, p.value_a := p.adjust(p.value, "fdr")] %>% 
  ggplot(aes(lev, estimate^2)) +
  geom_vline(xintercept = c(50, 200),  size = 0.2, color = "gray50") +
  # geom_point(data = ~.x[p.adjust(p.value, "fdr") < 0.01], aes(color = term)) +
  geom_line(aes(color = term, group = term, size = p.value_a <= 0.01)) +
  scale_x_level() +
  scale_y_continuous(r2, limits = c(0, 1)) +
  scale_size_manual("p-value", values = c("TRUE" = 1, 
                                      "FALSE" = 0.5), 
                    guide = "none") +
  scale_color_brewer(NULL, palette = "Dark2", labels = c(full = "SAM",
                                                         asym = "A-SAM",
                                                         sym = "S-SAM")) +
  facet_grid(part ~ cEOF) +
  coord_flip() +
  tag_facets("rc") +
  panel_background
```

>>>>

sam_r2 %>%
  .[, p.value_a := p.adjust(p.value, "fdr")] %>% 
  ggplot(aes(lev, estimate^2)) +
  geom_vline(xintercept = c(50, 200),  size = 0.2, color = "gray50") +
  # geom_point(data = ~.x[p.adjust(p.value, "fdr") < 0.01], aes(color = term)) +
  geom_line(data = ~copy(.x)[p.value_a > 0.01, estimate := NA], 
            aes(colour = stage(term, after_scale = scales::alpha(colour, 0.5))), 
            size = 2) +
  geom_line(aes(color = term, group = term)) +

  scale_x_level() +
  scale_y_continuous(r2, limits = c(0, 1)) +
  scale_size_manual("p-value", values = c("TRUE" = 1, 
                                      "FALSE" = 0.5), 
                    guide = "none") +
  scale_color_brewer(NULL, palette = "Dark2", labels = c(full = "SAM",
                                                         asym = "A-SAM",
                                                         sym = "S-SAM")) +
  facet_grid(part ~ cEOF) +
  coord_flip() +
  tag_facets("rc") +
  panel_background
```
